\documentclass[11pt,openright,a4paper]{report}
%%
%% This document template assumes you will use pdflatex.  If you are using
%% latex and dvipdfm to translate to pdf, insert dvipdfm into the options.
%%
\include{DissertationDefs}    %% These are the includes required for the doc 


\title{Mobile Technologies Supporting Corporate Loyalty Schemes}
\author{Henrik Stepanyan}
\date{Bachelor of Science in Computer Science with Honours and Industrial Placement\\The University of Bath\\May 2015}


\begin{document}


% Set this to the language you want to use in your code listings (if any)
\lstset{language=Java,breaklines,breakatwhitespace,basicstyle=\small}


\setcounter{page}{0}
\pagenumbering{roman}


\maketitle
\newpage


% Set this to the number of years consultation prohibition, or 0 if no limit
\consultation{0}
\newpage


\declaration{Mobile Technologies Supporting Corporate Loyalty Schemes}{Henrik Stepanyan}
\newpage


\abstract
Your abstract should appear here.  An abstract is a short
paragraph describing the aims of the project, what was
achieved and what contributions it has made.
\newpage


\tableofcontents
\newpage

\chapter*{Acknowledgements}
Add any acknowledgements here.
\newpage


\setcounter{page}{1}
\pagenumbering{arabic}



\chapter{Introduction}
%% Uncomment this to include a separate tex file wih the introduction contents
%\include{introduction.tex}

\chapter{Literature Survey}
\include{litreview}

\chapter{Requirements}
If you are doing a primarily software development project, this is the
chapter in which you review the requirements decisions and
critique the requirements process.


\chapter{Design}
This is the chapter in which you review your design decisions at various
levels and critique the design process.


\chapter{Implementation and Testing}
This is the chapter in which you review the implementation and testing
decisions and issues, and critique these processes.

Code can be output inline using \verb@\lstinline|some code|@.  For example,
this code is inline: \lstinline|public static int example = 0;|  (I have
used the character \verb@|@ as a delimiter, but any non-reserved character
not in the code text can be used.)

Code snippets can be output using the \verb|\begin{lstlisting} ... \end{lstlisting}|
environment with the code given in the environment.  For
example, consider listing \ref{Example-Code}, below.

\begin{lstlisting}[breaklines,breakatwhitespace,caption={Example code},label=Example-Code]
public static void main() {

  System.out.println("Hello World");

}
\end{lstlisting}

Code listings are produced using the package ``Listings''.  This has many
useful options, so have a look at the package documentation for further
ideas.


\chapter{Results}
This is the chapter in which you review the outcomes, and
critique the outcomes process.  You may include user evaluation here
too.


%%
%% Now we are back to the standard project contents that you should include
%%

\chapter{Conclusions}
%% Uncomment this to include a separate tex file wih the conclusion contents
%\include{conclusion.tex}

This is the chapter in which you review the major achievements in the
light of your original objectives, critique the process, critique your
own learning and identify possible future work.


\bibliography{ExampleBibFile}


\appendix

%%
%% Use the appendix for major chunks of detailed work, such as these. Tailor
%% these to your own requirements
%%

\chapter{Design Diagrams}

\chapter{User Documentation}

\chapter{Raw results output}

\chapter{Code}

%%
%% NOTE that for this to typeset correctly, ensure you use the pdflatex
%%      command in preference to the latex command.  If you do not have
%%      the pdflatex command, you will need to remove the landscape and
%%      multicols tags and just make do with single column listing output
%%

\begin{landscape}
\begin{multicols}{2}
\end{multicols}
\end{landscape}

\end{document}
