\textbf{Tell me quickly about your role}

I am a Business Analyst for the WREF (Worldwide Real Estate and Facilities) IT. My role within IT is facilitating any technological solutions required or requested by the WREF team; on or off-site.

\textbf{What are Bike Miles within COMPANY A}

Bike Miles within COMPANY A is a loyalty scheme for permanent COMPANY A staff members at 3 UK sites. Under the scheme, users who enter those sites are entitled to a sticker, which equates to £1 that can be spent in the bike shop (Evans Cycles). From the 3 sites that have the Bike Miles scheme, there are approximately 7000 staff members with 2100 users registered to the scheme of this, 800 active users (active users are those who have claimed more than £50 within the last year).This scheme is used to encourage our staff to get fit by riding to work, save the environment and help reduce the need for parking with the very limited spaces available at sites.

\textbf{What's the current scenario now}

The current scenario consists of the following:
\begin{enumerate}
\item Users come to the security barrier on site
\item They tear off a sticker
\item They then use their COMPANY A pass which opens the barrier, enabling them to enter the site
\item The sticker is put into a collecting paper card
\item The paper collection card is presented to the bike shop for money off 
\end{enumerate}

\textbf{What problems are there to tackle?}

With the existing there are a lot of problems to tackle as we believe people are abusing the system.
\begin{itemize}
\item Anyone can enter the scheme – Therefore we cannot track who is actually regularly riding their bikes onto sites. In regards to the 800 users listed above, they could potentially come into site in a car and still take a sticker.
\item People are taking more than one sticker at a time, with no security preventing the problem
\item Contractors are not entitled to the scheme, but could still take the stamps.
\item We believe there is a ‘black market’ for the stamps whereby users are taking the stamps and passing/selling them on to other staff members.
\end{itemize}

\textbf{What solutions have you guys thought about}

We have looked at other ideas to try and overcome the problem, but under current COMPANY A policy no new applications can be submitted into the current pool of apps. With that in mind a solution was required whereby staff could use their existing COMPANY A card to enter site and store Bike Money, or something similar with a smartphone:
\begin{itemize}
\item COMPANY As corporate device is the iPhone, an application with a QR code scanner which increments on a daily basis upon entering site
\item NFC solution with sticker on the back of existing staff card – Or with the new iPhone 6 this is already incorporated.
\item Fingerprint scanner (but no new applications)
\end{itemize}

\textbf{What do you think of this solution? ( The corporate loyalty app)}

For this solution to be feasible and useful, it would need to be:
\begin{itemize}
\item Available for all of our permanent staff to use
\item Easy integration for further sites and users globally
\item Good usability aspects. COMPANY A has 100,000 staff members with a variety of demographics, therefore all users should find it easy to use and better than the existing process
\item The system would need to increment on a daily basis when the staff members enter site (once a day only)
\end{itemize}
The corporate loyalty scheme is a great idea. Not only could it combat the issue of Bike Miles, as listed above, but it could also be used in conjunction with a lot of the other internal schemes that we have on site, such as Coffee loyalty scheme, gym membership, COMPANY A product store discounts (including online) etc.

\textbf{Could it be considered by COMPANY A?}

COMPANY A are always looking to improve, therefore if a product is received that significantly improves an existing process / technology it may be considered. Mobile phone applications have become more popular in general in recent years and this has rubbed off on COMPANY A staff members to change their perception (who previously were against mobile technologies). Also off the back of our recent success in winning an award for the Best Use of Mobile Technology Award (COMPANY A SiteMap App) we believe that mobile products can enhance our reputation internally and externally.
